%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1, 21 November 2016) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options. 
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}
\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{fontawesome}
\usepackage{hyperref}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{RedFox}{RGB}{195, 88, 23}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{RedFox}
\colorlet{accent}{RedFox}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Mirjalal TALISHINSKI}
\tagline{Android Developer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \location{Baku, Azerbaijan}
  \phone{tel:+994777511512}{+994 777 511 512}
  \mailaddress{mailto:mirjalal.talishinski@gmail.com}{mirjalal.talishinski@gmail.com}\\
  \github{https://github.com/mirjalal}{mirjalal}
  \stackoverflow{https://stackoverflow.com/u/4057688}{mirjalal}
  \linkedin{https://www.linkedin.com/in/mirjalaltalishinski}{mirjalaltalishinski}
}

%% Make the header extend all the way to the right, if you want. Extend the right margin by 8cm (=6.8cm marginparwidth + 1.2cm marginparsep)
\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Android Developer}{\href{https://tayqatech.com}{TayqaTech Ltd}}{July 2020 -- Ongoing}{Baku, Azerbaijan}
\begin{itemize}
\item We have created \& published a B2B E-Commerce Mobile application and also maintaining and supporting that application.
\item As a developer I learned how to create complex multi-module app.
\item Published app: \playstore{https://play.google.com/store/apps/details?id=com.tayqatech.ecom}{Sincab}
\end{itemize}

\divider

\cvevent{Android Developer}{Freelancer}{May 2020 -- Ongoing}{Remote}
\begin{itemize}
\item Currently, I am working on a variety of projects as a freelancer of which includes developing a retail banking app for one of the local banks and several enterprise resource planning and marketing apps.
\item Published apps: \playstore{https://play.google.com/store/apps/details?id=az.btb.mobilebanking}{BTB Mobile}
\end{itemize}

\divider

\cvevent{Android Developer}{\href{certoclav.com/en}{CertoClav GmBH}}{Nov 2019 -- May 2020}{Linz, Austria (Remote)}
\begin{itemize}
\item Wrote unit test and debugged critical application issues such as crashes, memory leaks. Performed bug fixes and added new features.
\item Implemented new generic product components for EU clients.
\item Worked closely with R\&D of the clients \& I finished all of the tasks a month before the deadline (as a result our clients got their FDA Certificates).
\end{itemize}
\divider

\cvevent{Android Developer}{\href{https://rabita.az/en/index}{Data Processing Center}}{Aug 2018 -- Nov 2019}{Baku, Azerbaijan}
\begin{itemize}
\item Provided weekly progress report to executive staff, ensuring that all parties were informed of milestones.
\item Focused heavily on learning and growing development skills using SOLID and TDD practices in an Agile development process.
\item Published app: \playstore{https://play.google.com/store/apps/details?id=com.mhm.sxm.edocverifier}{EDoc Verifier}
\end{itemize}

\divider

\cvevent{Software Developer}{\href{http://kiber.az/}{Kiber Ltd}}{Apr 2013 -- Jul 2017}{Baku, Azerbaijan}
\begin{itemize}
\item Led team of 5 developers in analysis and rebuild of software from beginning design through completion.
\item Developed object-oriented software, including multi-platform software (desktop, web and Android) for use in ERP industry.
\item Developed Android application for internal project to use in the company.
\item Optimized, managed and made relevant changes in existed applications.
\end{itemize}


\clearpage

\end{document}
